Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White Dwarf Progenitors

### 2018-12-26 paper/ms.tex
Bunch of changes and additions from a session sitting with Carlyn. Added new figures for the initial conditions of the simulations and the comparison between the estimated yields between the C/O and hybrid models. Also atted the poster document for future reference.

Supernovae are classified observationally 
by their light curves and spectra~\citep{minkowski41,bertola64,porterfilippenko87,
wheelerharkness1990conf,Fili97}, with the type Ia designation following from
the absence of H in the spectrum and the presence of a specific Si 
line~\citep{filippenko:optical,hillebrandt.niemeyer:type}. These events
have been associated with C burning under degenerate conditions
for some time~\citep{hoylefowler60,arnett.truran.ea:nucleosynthesis},
but discerning the setting(s) of these events is proving difficult
and remains the subject of active research. At present there are three
widely-accpeted scenarios: the {\em single degenerate} scenario,
the {\em double detonation} or {\em sub-Chandrasekhar} scenario, 
the {\em white dwarf merger} or {\em double degenerate} scenario.
We briefly describe these in the subsection that follows. `
Also see~\citet{hillebrandt.niemeyer:type,howell2011,hillebrandtetal2013,calderetal2013}
for additional discussion.

@@

@@

We used MESA, a 1-D stellar evolution code, to create the hybrid
model. We made the hybrid model have the same central temperature
and density as the classic model.

We found that the most abundant isotopes in the model were C12, O16,
Ne20. There were a few other isotopes that were added to form Ne22
later. We saw that  ….

Plotting the density verses solar radii, we found that the densest part
of the star is in the center slowly decreasing until it hits 0 at the
outer edge of the star.

In order to see where we should ignite the flame, we plotted the
temperature profile. It was found that the peak temperature is at the
center of the star, therefore, it was obvious to ignite the flame in
the core. (PUT IN TEMP PROFILE)

\subsection{Created 2D model from 1-D model}

We mapped our hybrid model to the FLASH grid. In order to convert our 1-D
MESA model into FLASH, which is a 2-D code, we needed symmetric nuclear
matter. This means that the ratio of neutrons to protons in the nuclei
must be the same ratio as in the mesa profile. This is because the amount
of extra neutrons around is important when burning the star because that
determines how much neutron rich isotopes the burning produces.

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figures/ni56_yield_cum_dist.png}
\caption{\label{fig:cumdist}
A plot of the estimated \Ni{56} yield as a function of the final, burned mass
for all CO and Hybrid runs. The Hybrid model is shown in red, and the CO
model is shown in blue. As it is shown, the CO model has a higher final mass
then the Hybrid model. 
}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{figures/ni56_vs_time_hybrid.png}
\caption{\label{fig:nithybrid}
Estimated \Ni{56} mass for Hybrid Model
}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{figures/ni56_vs_time_CO.png}
\caption{\label{fig:nitco}
Estimated \Ni{56} mass for CO Model
}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figures/ni56_yield_vs_mass_at_high_dens_v2.png}
\caption{\label{fig:masshighdens}
...
}
\end{figure}

>>>>

Supernovae are classified observationally 
by their light curves and spectra~\citep{minkowski41,bertola64,porterfilippenko87,
wheelerharkness1990conf,Fili97}, with the type Ia designation following from
the absence of H in the spectrum and the presence of a specific Si 
line~\citep{filippenko:optical,hillebrandt.niemeyer:type}. These events
have been associated with C burning under degenerate conditions
for some time~\citep{hoylefowler60,arnett.truran.ea:nucleosynthesis},
but discerning the setting(s) of these events is proving difficult
and remains the subject of active research. At present there are three
widely-accpeted scenarios: the {\em single degenerate} scenario,
the {\em double detonation} or {\em sub-Chandrasekhar} scenario, 
the {\em white dwarf merger} or {\em double degenerate} scenario.
We briefly describe these in the subsection that follows. `
Also see~\citet{hillebrandt.niemeyer:type,howell2011,hillebrandtetal2013,calderetal2013,roepkesim2018}
for additional discussion.

@@

Explosions from hybrid models \citet{kromeretal2015,bravoetal2016,willcoxetal2016}

@@

A hybrid white dwarf model constructed with the one-dimensional stellar 
evolution code MESA~\citep{mesa1,mesa2,mesa3,mesa3e} served as the 
initial conditions for the simulations of supernova explosions presented
in this work~\citep{brooksetal2017}.
The hybrid model was constructed to have conditions as similar a possible
to a ``classic" C/O model and the two shared the same central temperature
and density.  Figure~\ref{fig:init_conds} shows the density and temperature
profiles of the two initial one-dimensional models. 
\begin{figure}
\includegraphics[width=\columnwidth]{figures/initial_conds.png}
\caption{\label{fig:init_conds}
	We used MESA, a 1-D stellar evolution code, to create the hybrid model. We made the hybrid model have the same central temperature and density as the classic model. 
 We found that the most abundant isotopes in the model were C12, O16, Ne20. There were a few other isotopes that were added to form Ne22 later. We saw that  ….
Plotting the density verses solar radii, we found that the densest part of the star is in the center slowly decreasing until it hits 0 at the outer edge of the star. 
In order to see where we should ignite the flame, we plotted the temperature profile. It was found that the peak temperature is at the center of the star, therefore, it was obvious to ignite the flame in the core. (PUT IN TEMP PROFILE)
}
\end{figure}
In both models, and unlike the hybrid models of~\citet{willcoxetal2016}, the central
temperature was the highest at the center of the star and accordingly the simulations 
began with central initions.

\subsection{Created two-dimensional models from one-dimensional models}

The two-dimensional simulations were performed with a modified version
of the FLASH code developed at the University of Chicago. CITE
The initial one-dimensional MESA models were mapped to the two-dimensional 
FLASH grid. MORE HERE.

An additional step in constructing the two-dimensional initial conditions
was aggregating nuclides representing neutron-rich metals. 
The most abundant isotopes in the model were C12, O16,
Ne20 CHECK NE@) IS SYMMETRIC, which are symmetric (the number of neutrons 
equals the number of protons). Similarly to~\citet{willcoxetal2016}, other 
neutron-rich isotopes in
the initial model were to form Ne22, which serves as a proxy for metallicty. 
MESA model into FLASH, which is a 2-D code, we needed symmetric nuclear
matter. This means that the ratio of neutrons to protons in the nuclei
must be the same ratio as in the mesa profile. This is because the amount
of extra neutrons around is important when burning the star because that
determines how much neutron rich isotopes the burning produces.

@@

The cumulative distribution of the \Ni{56} yield for the C/O and hybrid
simulations is presented in \ref{fig:cumdist}. 
The figure presents the estimated \Ni{56} yield as a function of the final burned 
mass. The results show that the C/O models have a higher burned mass than the
hybrid models for a given estimated mass of \Ni{56}. CHECK THIS.

\begin{figure}
\includegraphics[width=\columnwidth]{figures/ni56_yield_cum_dist.png}
\caption{\label{fig:cumdist}
A plot of the estimated \Ni{56} yield as a function of the final, burned mass
for all CO and Hybrid runs. The Hybrid models are shown in red, and the CO
models are shown in blue. As it is shown, the CO model has a higher final mass
then the Hybrid model. 
}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{figures/ni56_vs_time_hybrid.png}
\caption{\label{fig:nithybrid}
Estimated \Ni{56} mass vs.\ time for ten hybrid model explosion simulations. 
Shown are realizations 21-30. 
}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{figures/ni56_vs_time_CO.png}
\caption{\label{fig:nitco}
Estimated \Ni{56} mass vs.\ time for ten C/O model explosion simulations.
Shown are realizations 21-30. 
}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figures/ni56_yield_vs_mass_at_high_dens_v2.png}
\caption{\label{fig:masshighdens}
This is a plot of the estimated Ni56 yield vs. mass below 2e7 g/cc at the time of the DDT. 
The degree of expansion was found using the time at which the first detonation point occurred, and the mass at density less then 2e7 g/cc. The estimated Ni56 Yield is the final estimated mass of the model. 
Hybrid- Red
CO- Blue
For a given amount of mass at high density, the CO produces more Iron group elements then the Hybrid model.  
The rectangular regions show one stanadard deviation from the average for both the C/O and hybrid 
models (SEE DON'S PAPER)
}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{figures/compare.png}
\caption{\label{fig:compare}
The conversion of Ni56 to Iron group elements are more pronounced in my case. There are two assumptions as to why figure 6 is more pronounced in my paper then in Dons. 
First is that higher critical density leads to higher electron capture resulting in less Ni56 produced. Figure 4 shows that CO model has a stronger electron capture then the hybrid model. The second is that the central ignition leads to early burning at higher density. Both of these cases lead to more electron capture resulting in a larger difference in evolution between the models.
NEW: Production of 56Ni and mass burned to IGEs for CO (red) and
hybrid CONe (green) WD realizations. SAME AS DON'S FIG 18
}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{figures/compare_burned_mass.png}
\caption{\label{fig:compare}
SAME AS DON'S FIGURE 19.
C/O blue hybrid red.
Note that one of the C/O simulations presented did not complete.
}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{figures/compare_ratio.png}
\caption{\label{fig:compare_ratio}
Figure 8 shows the evolution of the materials for both models. It is determined that the CO model had the greatest amount of Ni56, then the other IGE materials, compared to the hybrid model.  
SAME AS DON'S FIGURE 20.
}
\end{figure}
